---
title: "mODa13"
description: |
  <b>Programme</b>
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

An outline schedule for the workshop is given below. **A full programme is available [here](static/programme.html)**.

The workshop will start with registration and a welcome reception/bbq on **Sunday evening (9 July; 18.00 - 20.00 in the common room/quad (B block) in Chamberlain Hall)**.

**Talks** all have 22.5 minute slots, and should be prepared to leave a little time for questions.

**Posters** will be displayed on Tuesday 11 July, and should be put up before the start of the workshop that day and taken down at the end of the day. They will be displyed on boards which are 1200mm x 1200mm in size.

```{r}
library(readr)
library(dplyr)
library(gt)
library(tidyr)
library(stringr)

prelim_data <- read_csv("../timetable/prelim_schedule.csv", show_col_types = FALSE)
prelim_data |> 
  mutate(Session = case_when(
    Session ==  "BBQ (18.00 - 20.00; Chamberlain Hall)" ~ "BBQ (18.00 - 20.00; Chamberlain Hall)",
    Session == "mODa 14" ~ "mODa 14",
    .default = str_to_title(Session)
    )) |>
  pivot_wider(names_from = Day, values_from = Session) |>
  mutate(across(1:6, \(x) str_replace_all(x, pattern = "Coffee break", replacement = "Coffee"))) |>
  mutate(across(1:6, \(x) str_replace_all(x, pattern = "Tea break", replacement = "Tea"))) |>
  gt() |>
  tab_header(
    title = "Outline schedule",
  ) |>
  sub_missing(missing_text = '') |>
  opt_row_striping() |>
    tab_options(
      table.width = pct(100)
    ) |>
    cols_label(
      Time = ""
    ) |>
  tab_style(
    style = cell_text(
      weight = "bold"
    ),
    location = cells_column_labels(columns = everything())
  ) |>
  cols_align(
    columns = Time,
    align = "left"
  ) |>
  tab_style(
    # Select object to modify
    locations = cells_title(groups = 'title'),
    # Specify text style
    style = list(
      cell_text(
        font=google_font(name = 'Bebas Neue'), 
        size='xx-large',
        color='#005C84'
  )))
```
